Bird beak's elaboration and innovation

### 2022-04-21 Analysis/04-Figure1_with_ellipse_scalling_and_8D_histograms.Rmd
Renamed figure Rmds to contain also analyses bits

```{r, echo = FALSE}
## Quick load
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
results <- shapespace_allbirds_lvl_superorder_order_results_list
rm(shapespace_allbirds_lvl_superorder_order_results_list)
```

@@

```{r}
## Plotting the ellipses
plot.one.ellipse <- function(data, name.col, x = TRUE, y = TRUE, main = "", legend = FALSE, with.phylo = FALSE) {

@@

```{r}
source("../Functions/covar.utilities.R")
box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure1_phylo_Dplot.pdf", height = box_size*2, width = box_size*2)

lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "", ylab = "", main = "")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)

covars_cent_tend <- lapply(sample.n(get.subsets(data, subset = "phylogeny")$covar, n), VCV.cent.tend, mean)
dim_var <- apply((get.one.axis(covars_cent_tend[[1]], axis = 1, level = 0.95)), 2, dist)
dim_var <- dim_var/max(dim_var)/10
x_start <- 0.2
y_start <- -0.1
buffer <- 0
for(one_dim in 1:length(dim_var)) {
    lines(x = c(x_start, x_start+dim_var[one_dim]), y = rep(y_start+buffer, 2), lwd = 3, col = "grey")
    buffer <- buffer - 0.02
}

dev.off()

>>>>

```{r, echo = FALSE}
## Quick load
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list_4k.rda")
results <- shapespace_allbirds_lvl_superorder_order_results_list
rm(shapespace_allbirds_lvl_superorder_order_results_list)
```

@@

```{r}
source("../Functions/covar.utilities.R")
## Plotting the ellipses
plot.one.ellipse <- function(data, name.col, x = TRUE, y = TRUE, main = "", legend = FALSE, with.phylo = FALSE) {

@@

```{r}
box_size <- 1.5
# pdf(file = "../Manuscript/Figures/Figure1_phylo_Dplot.pdf", height = box_size*2, width = box_size*2)

# lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
# plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "", ylab = "", main = "")
# abline(v = 0, col = "grey", lwd = 0.5)
# abline(h = 0, col = "grey", lwd = 0.5)

# covars_cent_tend <- lapply(sample.n(get.subsets(data, subset = "phylogeny")$covar, n), VCV.cent.tend, mean)
# dim_var <- apply((get.one.axis(covars_cent_tend[[1]], axis = 1, level = 0.95)), 2, dist)
# dim_var <- dim_var/max(dim_var)/10
# x_start <- 0.2
# y_start <- -0.1
# buffer <- 0
# for(one_dim in 1:length(dim_var)) {
#     lines(x = c(x_start, x_start+dim_var[one_dim]), y = rep(y_start+buffer, 2), lwd = 3, col = "grey")
#     buffer <- buffer - 0.02
# }

# dev.off()

### 2022-04-21 Analysis/05-Figure2_with_lambdas.Rmd
Renamed figure Rmds to contain also analyses bits

## Get the lambdas for all levels for the elaborations
overall_lambda_elaboration <- get.p.lambda(species = ploting_data$consensus_tree$tip.label, variable = ploting_data$median_elaborations, tree = ploting_data$consensus_tree, modelCIs = FALSE)
all_lambdas_elaboration <- lapply(group_species_names, lapply, function(x, tree, variable, ...) {cat(".") ; get.p.lambda(names(x), variable, tree, ...)},
                                  tree = ploting_data$consensus_tree,
                                  variable = ploting_data$median_elaborations,
                                  modelCIs = FALSE)
overall_lambda_innovation <- get.p.lambda(species = ploting_data$consensus_tree$tip.label, variable = ploting_data$median_innovations, tree = ploting_data$consensus_tree, modelCIs = FALSE)
all_lambdas_innovation <- lapply(group_species_names, lapply, function(x, tree, variable, ...) {cat(".") ; get.p.lambda(names(x), variable, tree, ...)},
                                  tree = ploting_data$consensus_tree,
                                  variable = ploting_data$median_innovations,
                                  modelCIs = FALSE)
## Make into a table
lambda_elaboration <- list(overall_lambda_elaboration$Lambda, lapply(all_lambdas_elaboration, lapply, function(X) return(X$Lambda)))
lambda_innovation <- list(overall_lambda_innovation$Lambda, lapply(all_lambdas_innovation, lapply, function(X) return(X$Lambda)))
lambda_table <- cbind(unlist(lambda_elaboration), unlist(lambda_innovation))
lambdas_superorder <- lambda_table[c(2: 9), ]
lambdas_order <- lambda_table[-c(1: 9), ]
```

>>>>

## Get the lambdas for all levels for the elaborations
overall_lambda_elaboration <- get.p.lambda(species = ploting_data$consensus_tree$tip.label, variable = ploting_data$median_elaborations, tree = ploting_data$consensus_tree, modelCIs = FALSE)
all_lambdas_elaboration <- lapply(group_species_names, lapply, function(x, tree, variable, ...) {cat(".") ; get.p.lambda(names(x), variable, tree, ...)},
                                  tree = ploting_data$consensus_tree,
                                  variable = ploting_data$median_elaborations,
                                  modelCIs = FALSE)
overall_lambda_innovation <- get.p.lambda(species = ploting_data$consensus_tree$tip.label, variable = ploting_data$median_innovations, tree = ploting_data$consensus_tree, modelCIs = FALSE)
all_lambdas_innovation <- lapply(group_species_names, lapply, function(x, tree, variable, ...) {cat(".") ; get.p.lambda(names(x), variable, tree, ...)},
                                  tree = ploting_data$consensus_tree,
                                  variable = ploting_data$median_innovations,
                                  modelCIs = FALSE)
## Make into a table
lambda_elaboration <- list(overall_lambda_elaboration$Lambda, lapply(all_lambdas_elaboration, lapply, function(X) return(X$Lambda)))
lambda_innovation <- list(overall_lambda_innovation$Lambda, lapply(all_lambdas_innovation, lapply, function(X) return(X$Lambda)))
lambda_table <- cbind(unlist(lambda_elaboration), unlist(lambda_innovation))
lambda_table <- data.frame(rbind(c("class", "aves"), do.call(rbind, strsplit(rownames(lambda_table), split = "\\."))), lambda_table)
colnames(lambda_table) <- c("level", "name", "elaboration", "innovation")
rownames(lambda_table) <- lambda_table$name
```
